Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-22 WSSSPE4_report/WSSSPE4_report.tex
Add my affiliation.
some more work on lightning talk descriptions... still not done

    \item \textbf{Sandra Gesing, Maytal Dahan, Linda B.~Hayden, Katherine Lawrence,
    Suresh Marru, Marlon Pierce, Nancy Wilkins-Diehr, and Michael Zentner:
    \emph{The Science Gateways Community Institute - Supporting Communities to
    Achieve Sustainability for Their Science Gateways}}~\cite{Gesing:2016ws}.
    Description

    \item \textbf{Karthik Ram\textsuperscript{\textasteriskcentered}, Noam Ross,
    and Scott Chamberlain: \emph{A model for
    peer review and onboarding research software}}~\cite{Ram:2016ws}.
    Description
    %Some people greatly encouraged to only submit to a journal code that has been peer reviewed

    \item \textbf{Frank L\"{o}ffler and Steven Brandt\textsuperscript{\textasteriskcentered}:
    \emph{A vision of computing in 10+ years}}~\cite{Loffler:2016ws}.
    Description
    %“We (need to) decouple science from numerical methods and optimization” Hard open problem.

    \item \textbf{Daniel S.~Katz, Kyle E.~Niemeyer\textsuperscript{\textasteriskcentered},
    Arfon M.~Smith, and the FORCE11 Software Citation Working Group:
    \emph{Software Citation: Process, Principles, and Implementation}}~\cite{Katz:2016ws}.
    Description

    \item \textbf{Ray Idaszak\textsuperscript{\textasteriskcentered},
    David G.~Tarboton, Hong Yi, Michael Stealey,
    Pabitra Dash, Alva Couch, Daniel P.~Ames, Jeffery S.~Horsburgh, Tony Castronova,
    Jon Goodall, Mohamed Morsy, Venkatesh Merwade, Mauriel Ramirez, Tian Gan,
    Drew (Zhiyu) Li, Jeff Sadler, Shawn Crawley, Zhaokun Xue, Lan Zhao, Carol Song,
    Christina Bandaragoda: \emph{HydroShare - A Case Study in Software Engineering
    Best Practices and Culture Change for Developing Sustainable Community
    Software}}~\cite{Idaszak:2016ws}.
    Description

    \item \textbf{Lorraine Hwang\textsuperscript{\textasteriskcentered},
    Wolfgang Bangerth, Timo Heister, and Louise Kellogg:
    \emph{ASPECT: Hackathons as an Example of Sustaining an Open Source
    Community}}~\cite{Hwang:2016ws}.
    Description

    \item \textbf{Carole Goble: \emph{A Simple Profiling Framework for Software
    User-Producer Maturity Review}}~\cite{Goble:2016ws}.
    Description

    \item \textbf{Stephan Druskat: \emph{A proposal for the measurement and
    documentation of research software sustainability in interactive metadata
    repositories}}~\cite{Druskat:2016ws}.
    Description

    \item \textbf{Mistral Contrastin, Matthew Danish,
    Dominic Orchard\textsuperscript{\textasteriskcentered}, and
    Andrew Rice: \emph{Supporting software sustainability with
    lightweight specifications}}~\cite{Contrastin:2016ws}.
    Description

    \item \textbf{Alice Allen, Cecilia Aragon, Christoph Becker, Jeffrey Carver,
    Andrei Chi\c{s}, Benoit Combemale, Mike Croucher, Kevin Crowston, Daniel Garijo,
    Ashish Gehani, Carole Goble\textsuperscript{\textasteriskcentered},
    Robert Haines, Robert Hirschfeld, James Howison,
    Kathryn Huff, Caroline Jay, Daniel S.~Katz, Claude Kirchner, Kateryna Kuksenok,
    Ralf L\"{a}mmel, Oscar Nierstrasz, Matt Turk, Rob van Nieuwpoort, Matthew Vaughn,
    and Jurgen Vinju: \emph{``I solemnly pledge'': A Manifesto for Personal
    Responsibility in the Engineering of Academic Software}}~\cite{AAllen:2016ws}.
    Description

    \item \textbf{Eric L.~Seidel\textsuperscript{\textasteriskcentered}
    and Gabrielle Allen: \emph{Bringing Techniques from Software Engineering
    into Scientific Software}}~\cite{Seidel:2016ws}.
    Description

>>>>

    \item \textbf{Sandra Gesing, Maytal Dahan, Linda B.~Hayden, Katherine Lawrence,
    Suresh Marru, Marlon Pierce, Nancy Wilkins-Diehr, and Michael Zentner:
    \emph{The Science Gateways Community Institute - Supporting Communities to
    Achieve Sustainability for Their Science Gateways}}~\cite{Gesing:2016ws}.
    \note{Description}

    \item \textbf{Karthik Ram\textsuperscript{\textasteriskcentered}, Noam Ross,
    and Scott Chamberlain: \emph{A model for
    peer review and onboarding research software}}~\cite{Ram:2016ws}.
    \note{Description}
    %Some people greatly encouraged to only submit to a journal code that has been peer reviewed

    \item \textbf{Frank L\"{o}ffler and Steven Brandt\textsuperscript{\textasteriskcentered}:
    \emph{A vision of computing in 10+ years}}~\cite{Loffler:2016ws}.
    \note{Description}
    %“We (need to) decouple science from numerical methods and optimization” Hard open problem.

    \item \textbf{Daniel S.~Katz, Kyle E.~Niemeyer\textsuperscript{\textasteriskcentered},
    Arfon M.~Smith, and the FORCE11 Software Citation Working Group:
    \emph{Software Citation: Process, Principles, and Implementation}}~\cite{Katz:2016ws}.
    This talk described the timeline of activities of the FORCE11 Software Citation
    Working Group and the principles of software citation established by the group.
    Niemeyer, one of the working group cochairs, also discussed the paper published
    describing the principles~\cite{Smith:2016sc}, and the remaining steps of the
    working group before sunsetting it and spinning up a new Software Citation
    Implementation Working Group.

    \item \textbf{Ray Idaszak\textsuperscript{\textasteriskcentered},
    David G.~Tarboton, Hong Yi, Michael Stealey,
    Pabitra Dash, Alva Couch, Daniel P.~Ames, Jeffery S.~Horsburgh, Tony Castronova,
    Jon Goodall, Mohamed Morsy, Venkatesh Merwade, Mauriel Ramirez, Tian Gan,
    Drew (Zhiyu) Li, Jeff Sadler, Shawn Crawley, Zhaokun Xue, Lan Zhao, Carol Song,
    Christina Bandaragoda: \emph{HydroShare - A Case Study in Software Engineering
    Best Practices and Culture Change for Developing Sustainable Community
    Software}}~\cite{Idaszak:2016ws}.
    \note{Description}

    \item \textbf{Lorraine Hwang\textsuperscript{\textasteriskcentered},
    Wolfgang Bangerth, Timo Heister, and Louise Kellogg:
    \emph{ASPECT: Hackathons as an Example of Sustaining an Open Source
    Community}}~\cite{Hwang:2016ws}.
    \note{Description}

    \item \textbf{Carole Goble: \emph{A Simple Profiling Framework for Software
    User-Producer Maturity Review}}~\cite{Goble:2016ws}.
    \note{Description}

    \item \textbf{Stephan Druskat: \emph{A proposal for the measurement and
    documentation of research software sustainability in interactive metadata
    repositories}}~\cite{Druskat:2016ws}.
    \note{Description}

    \item \textbf{Mistral Contrastin, Matthew Danish,
    Dominic Orchard\textsuperscript{\textasteriskcentered}, and
    Andrew Rice: \emph{Supporting software sustainability with
    lightweight specifications}}~\cite{Contrastin:2016ws}.
    \note{Description}

    \item \textbf{Alice Allen, Cecilia Aragon, Christoph Becker, Jeffrey Carver,
    Andrei Chi\c{s}, Benoit Combemale, Mike Croucher, Kevin Crowston, Daniel Garijo,
    Ashish Gehani, Carole Goble\textsuperscript{\textasteriskcentered},
    Robert Haines, Robert Hirschfeld, James Howison,
    Kathryn Huff, Caroline Jay, Daniel S.~Katz, Claude Kirchner, Kateryna Kuksenok,
    Ralf L\"{a}mmel, Oscar Nierstrasz, Matt Turk, Rob van Nieuwpoort, Matthew Vaughn,
    and Jurgen Vinju: \emph{``I solemnly pledge'': A Manifesto for Personal
    Responsibility in the Engineering of Academic Software}}~\cite{AAllen:2016ws}.
    \note{Description}

    \item \textbf{Eric L.~Seidel\textsuperscript{\textasteriskcentered}
    and Gabrielle Allen: \emph{Bringing Techniques from Software Engineering
    into Scientific Software}}~\cite{Seidel:2016ws}.
    \note{Description}
